\begin{thebibliography}{50}
\bibitem {CurrentParsTechn} \emph{Mark G.J. van den Brand, Alex Sellink, Chris Verhoef} 
        Current Parsing Techniques in Software Renovation Considered Harmful.// IWPC '98: Proceedings of the 6th International Workshop on Program Comprehension. - IEEE Computer Society, Washington,1998.
        
\bibitem {FS} \emph http://www.research.microsoft.com/fsharp (дистрибутивы и документация по языку F\#)

\bibitem {Diploma} \emph{Чемоданов И.С.} Генератор синтаксических анализаторов  для решения задач автоматизированного реинжиниринга программ.

\bibitem {Practical Guide} \emph{Dick Grune, Ceriel Jacobs} PARSING TECHNIQUES A Practical Guide

\bibitem {DrgBook} \emph {Ахо А., Сети Р., Ульман Дж.} Компиляторы: принципы, технологии, инструменты.  М:. Издательский дом <Вильямс>2003. 768 с.

\bibitem {Jade} \emph {Ronald Veldena} Jade, a recursive ascent LALR(1) parser generator. September 8,1998

\bibitem {Non-det-rec-asc} \emph {Rene Leermakers} Non-deterministic Recursive Ascent Parsing. Philips Research Laboratories,
      P.O. Box 80.000, 5600 JA Eindhoven, The Netherlands. 

\bibitem {RECURSIVE-ASCENT PARSING} \emph {Larry Morell, David Middleton} RECURSIVE-ASCENT PARSING. Arkansas Tech    
       University Russellville, Arkansas. 

\bibitem {RecursiveAscentParsing} \emph {Lex Augusteijn} Recursive Ascent Parsing (Re: Parsing techniques). lex@prl.philips.nl (Lex Augusteijn)
      Mon, 10 May 1993 07:03:39 GMT 

\bibitem {ASF+SDF} \emph {} http://www.cwi.nl/projects/MetaEnv (сайт разработчиков ASF+SDF)

\bibitem {Bison} \emph {} http://www.gnu.org/software/bison (сайт разработчиков Bison)

\bibitem {Elkhound} \emph {} http://www.cs.berkeley.edu/smcpeak/elkhound (сайт разработчиков Elkhound )
\end{thebibliography}
